Performing graph-based clustering with rOpenScPCA

### 2024-12-17 analyses/hello-clusters/01_perform-evaluate-clustering.Rmd
update how metadata clustering params are presented, printed, and used

ScPCA cell metadata already contains a column called `cluster` with results from an automated clustering. 
These clusters were calculated using `bluster`, the same tool that `rOpenScPCA` uses. 
We can see the parameters it used from the SCE object's metadata; all other parameters were left at their default values.

```{r extract cluster params}
# Print the clustering algorithm used
metadata(sce)$cluster_algorithm

# Print the weighting scheme
metadata(sce)$cluster_weighting

# Print the number of nearest neighbors
metadata(sce)$cluster_nn
```

@@

When running `rOpenScPCA::calculate_stability()`, we'll specify the same parameters originally used to build the clusters.
Generally speaking, we only recommend evaluating clusters with `rOpenScPCA::calculate_stability()` if you know the original parameters used.

```{r scpca stability}
scpca_stability_df <- rOpenScPCA::calculate_stability(
  sce,
  scpca_cluster_df,
  # provide ScPCA clustering parameters
  algorithm = "louvain",
  weighting = "jaccard",
  nn = 20
)
```

>>>>

ScPCA cell metadata already contains a column called `cluster` with results from an automated clustering. 
These clusters were calculated using `bluster`, the same tool that `rOpenScPCA` uses. 
The specifications used for this clustering are stored in the SCE object's metadata, as follows; note that all other clustering parameters were left at their default values.

* `metadata(sce)$cluster_algorithm`: The clustering algorithm used
* `metadata(sce)$cluster_weighting`: The weighting scheme used
* `metadata(sce)$cluster_nn`: The number of nearest neighbors used

You can see all their values here:

```{r extract cluster params}
# Print clustering specifications
metadata(sce)[c("cluster_algorithm", "cluster_weighting", "cluster_nn")]
```

@@

When running `rOpenScPCA::calculate_stability()`, we'll specify the same parameters originally used to build the clusters by extracting them from the metadata.
We'll need to ensure the provided arguments are lowercase, as well.

Generally speaking, we only recommend evaluating clusters with `rOpenScPCA::calculate_stability()` if you know the original parameters used.

```{r scpca stability}
scpca_stability_df <- rOpenScPCA::calculate_stability(
  sce,
  scpca_cluster_df,
  # provide ScPCA clustering parameters by extracting from the SCE metadata
  algorithm = tolower(metadata(sce)$cluster_algorithm),
  weighting = tolower(metadata(sce)$cluster_weighting),
  nn = metadata(sce)$cluster_nn
)
```
